---
title: "Presentation Ninja"
subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Yihui Xie"
  - "Garrick Aden-Buie"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
library(xaringanExtra)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(sugrrants) # create calendar
library(leaflet)
library(lubridate)
library(ggthemes)
```


```{r xaringan-themer, include=FALSE, warning=FALSE}
style_solarized_light()
```

background-image: url(https://i.insider.com/5c17d38801c0ea08470c8fb2?width=700&format=jpeg&auto=webp)

# Group member

### Yiwen Jiang (yjia0021) 
### Yuheng Cui (ycui0008)

.footnote[
Image source: Insider https://i.insider.com/5c17d38801c0ea08470c8fb2?width=700&format=jpeg&auto=webp
]

---

# Topic

### How does relative humidity in Melbourne change throughout the day and year? When is it most uncomfortable to walk around the city?



---

#### Data

```{r read-data, echo = FALSE, message=FALSE,warning=FALSE}
climate_locations <- read_csv(here::here("data/Microclimate_Sensor_Locations.csv"))
climate_readings <- read_csv(here::here("data/Microclimate_Sensor_Readings.csv"))
```

```{r use-panel,include=FALSE}
use_panelset()
```

.panelset[
.panel[.panel-name[climate_locations.csv]
```{r view-location, echo = FALSE}
climate_locations %>% 
  kable() %>% 
  kable_material(c("striped", "hover"), font_size = 9, full_width = F)
```

This dataset is small and only has 5 rows and 6 columns.


]

.panel[.panel-name[climate_readings.csv]
```{r view-readings, echo = FALSE}
climate_readings %>% 
  head() %>% 
  kable() %>% 
  kable_material(c("striped", "hover"), font_size = 9, full_width = F)
```

This dataset has `r nrow(climate_readings)` rows and `r ncol(climate_readings)` columns.

* `value`: Value of reading
* `type`: type of sensor
]
.panel[.panel-name[What we need]
```{r readings-type, echo=FALSE}
data.frame(type = c("TPH.RH", "TPH.RH-EPA-1h"),
           measures = c("Relative humidity (RH) every 15 mins",
                        "Relative humidity (RH) every 1 hour"),
           range = rep("1 - 100", 2),
           unit = rep("%", 2)
           ) %>% 
  kbl() %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, background = "yellow")

```

**TPH**: Temperature, Pressure and Humidity

About `climate_readings` data: There may be situations where no readings are reported for all sensors or only some readings are reported at a particular site. 



]

]

.footnote[

source from [Microclimate Sensor Readings](https://data.melbourne.vic.gov.au/Environment/Microclimate-Sensor-Readings/u4vh-84j8?src=featured_banner) and [Microclimate Sensor Locations](https://data.melbourne.vic.gov.au/Environment/Microclimate-Sensor-Locations/irqv-hjr4)]


---

#### Overview of the sensors' locations

```{r sensor-location, echo = FALSE, cache=TRUE}
leaflet() %>%
  addTiles() %>%
  addMarkers(
    lng = climate_locations[1, ]$longitude,
    lat = climate_locations[1, ]$latitude,
    label = climate_locations[1, ]$description,
    popup = climate_locations[1, ]$site_id,
    labelOptions = labelOptions(
      noHide = T,
      style = list(
        "color" = "black",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )
    )
  ) %>%
  addMarkers(
    lng = climate_locations[2, ]$longitude,
    lat = climate_locations[2, ]$latitude,
    label = climate_locations[2, ]$description,
    popup = climate_locations[2, ]$site_id,
    labelOptions = labelOptions(
      # direction = "bottom",
      # noHide = T,
      style = list(
        "color" = "black",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )
    )
  ) %>%
  addMarkers(
    lng = climate_locations[3, ]$longitude,
    lat = climate_locations[3, ]$latitude,
    label = climate_locations[3, ]$description,
    popup = climate_locations[3, ]$site_id,
    labelOptions = labelOptions(
      # direction = "bottom",
      # noHide = T,
      style = list(
        "color" = "black",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )
    )
  ) %>%
  addMarkers(
    lng = climate_locations[4, ]$longitude,
    lat = climate_locations[4, ]$latitude,
    label = climate_locations[4, ]$description,
    popup = climate_locations[4, ]$site_id,
    labelOptions = labelOptions(
      # direction = "bottom",
      noHide = T,
      style = list(
        "color" = "black",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )
    )
  ) %>%
  addMarkers(
    lng = climate_locations[5, ]$longitude,
    lat = climate_locations[5, ]$latitude,
    label = climate_locations[5, ]$description,
    popup = climate_locations[5, ]$site_id,
    labelOptions = labelOptions(
      direction = "bottom",
      noHide = T,
      style = list(
        "color" = "black",
        "font-family" = "serif",
        "font-style" = "italic",
        "box-shadow" = "3px 3px rgba(0,0,0,0.25)",
        "font-size" = "12px",
        "border-color" = "rgba(0,0,0,0.5)"
      )
    )
  )

```




---

#### RH - daily (from west to east)





.panelset[


.panel[.panel-name[arc1047]
```{r daily_rh3, echo=FALSE,warning=FALSE,message=FALSE,cache=TRUE}

df1 <- climate_readings %>% 
  separate(local_time,
           into = c("date", "time"),
           " ") 

climate_readings_hrly <- df1 %>% 
  mutate(date = as.Date(date, format = "%Y/%m/%d"),
         time = hms::as.hms(time)) %>% 
  filter(type == "TPH.RH-EPA-1h") %>% 
  mutate(time = hour(time),
         time = as.double(time))

cal_3 <- climate_readings_hrly %>% 
  filter(site_id == "arc1047") %>% 
  frame_calendar(x = time, y = value,
                 date = date,
                 ncol = 4) %>% 
  ggplot(aes(x = .time,
             y = .value,
             group = date)) +
  geom_line()


prettify(cal_3)


```
]


.panel[.panel-name[arc1046]
```{r daily_rh2, echo=FALSE,warning=FALSE,message=FALSE,cache=TRUE}
cal_2 <- climate_readings_hrly %>% 
  filter(site_id == "arc1046") %>% 
  frame_calendar(x = time, y = value,
                 date = date,
                 ncol = 4) %>% 
  ggplot(aes(x = .time,
             y = .value,
             group = date)) +
  geom_line() 


prettify(cal_2)



```
]


.panel[.panel-name[arc1048]
```{r daily_rh4, echo=FALSE,warning=FALSE,message=FALSE,cache=TRUE}
cal_4 <- climate_readings_hrly %>% 
  filter(site_id == "arc1048") %>% 
  frame_calendar(x = time, y = value,
                 date = date,
                 ncol = 4) %>% 
  ggplot(aes(x = .time,
             y = .value,
             group = date)) +
  geom_line() 


prettify(cal_4)



```
]



.panel[.panel-name[arc1050]
```{r daily_rh5, echo=FALSE,warning=FALSE,message=FALSE,cache=TRUE}
cal_5 <- climate_readings_hrly %>% 
  filter(site_id == "arc1050") %>% 
  frame_calendar(x = time, y = value,
                 date = date,
                 ncol = 4) %>% 
  ggplot(aes(x = .time,
             y = .value,
             group = date)) +
  geom_line() 


prettify(cal_5)



```
]



.panel[.panel-name[arc1045]
```{r daily_rh1, echo=FALSE,warning=FALSE,message=FALSE,cache = TRUE}


cal_1 <- climate_readings_hrly %>% 
  filter(site_id == "arc1045") %>% 
  frame_calendar(x = time, y = value,
                 date = date,
                 ncol = 4) %>% 
  ggplot(aes(x = .time,
             y = .value,
             group = date)) +
  geom_line() 
  # facet_wrap(~ site_id, ncol = 2)


prettify(cal_1)

```
]




]

---

#### Daily average RH


```{r,echo = FALSE, message=FALSE}
climate_readings_hrly %>% 
  group_by(date, site_id) %>% 
  summarise(value_mean = mean(value)) %>% 
  ungroup() %>% 
  ggplot(aes(x = date, y = value_mean)) +
  geom_line() +
  scale_x_date(date_breaks = "1 month")+
  geom_vline(xintercept = as.Date("2020-01-01"), size = 1, color = "red")+
  geom_hline(yintercept = c(30, 60), color = "green", size = 1)+
  annotate("text", x = as.Date("2020-05-01"), y = 50, label = "Comfort Zone", color = "green", size = 15)+
  labs(y = "RH (%)", x = "", title = "Daily Relative Humidity", subtitle = "RH range is from 1 to 100") +
  geom_smooth()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
















